---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Alberte Seeberg"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.

2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

3) Do you observe differences in coordination between conditions? Report the models and results.

4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment

### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)
- Can you eye-ball which condition if any displays more physiological coordination?

- Run crqa on heart rate and respiration data (find parameters, run crqa)
- Does this tell you more than just eyeballing the plots?

```{r}
#Setting working directory
setwd("~/Desktop/3. Semester/Experimental methods 3/Portfolio 4")

#Loading data
PairSync=read.csv("CleanData/Study2_G5_T1_Synchronous.csv")
PairTurn=read.csv("CleanData/Study2_G5_T2_TurnTaking.csv")
PairCon=read.csv("CleanData/Study2_G5_T3_Conversation.csv")

#Loding relevant packages
library(ggplot2)
library(groupdata2)
library(dplyr)
library(gridExtra)
library(crqa)
library(stringr)
library(readr)
library(tidyverse)
library(lmerTest)

#Creating plots for respiration
plot1=ggplot(PairCon, aes(x=time, y=Resp1)) + geom_line(color="blue4") + geom_line(aes(x=time, y=Resp2), color="firebrick3") + theme(legend.position="none")

plot2=ggplot(PairTurn, aes(x=time, y=Resp1)) + geom_line(color="blue4") + geom_line(aes(x=time, y=Resp2), color="firebrick3") + theme(legend.position="none")

plot3=ggplot(PairSync, aes(x=time, y=Resp1)) + geom_line(color="blue4") + geom_line(aes(x=time, y=Resp2), color="firebrick3") + theme(legend.position="none")

#Creating plots for heart rate
plot4=ggplot(PairCon, aes(x=time, y=HR1)) + geom_line(color="coral") + geom_line(aes(x=time, y=HR2), color="cyan4") + theme(legend.position="none")

plot5=ggplot(PairTurn, aes(x=time, y=HR1)) + geom_line(color="coral") + geom_line(aes(x=time, y=HR2), color="cyan4") + theme(legend.position="none")

plot6=ggplot(PairSync, aes(x=time, y=HR1)) + geom_line(color="coral") + geom_line(aes(x=time, y=HR2), color="cyan4") + theme(legend.position="none")

#Downsampling
PairCon = PairCon %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))

PairSync = PairSync %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))

PairTurn = PairTurn %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))

#Removing outliers
removeOuts = function(ts,threshold){
   ts[ts > (mean(ts,na.rm=T) +  
           (threshold*sd(ts,na.rm=T))) | 
        ts < (mean(ts,na.rm=T) -
           (threshold*sd(ts,na.rm=T)))] = mean(ts,na.rm=T)  
   return(ts)}
threshold=2.5
PairCon$HR1=PairCon$HR1=removeOuts(PairCon$HR1,threshold)
PairSync$HR1=PairSync$HR1=removeOuts(PairSync$HR1,threshold)
PairTurn$HR1=PairTurn$HR1=removeOuts(PairTurn$HR1,threshold)
PairCon$HR2=PairCon$HR2=removeOuts(PairCon$HR2,threshold)
PairSync$HR2=PairSync$HR2=removeOuts(PairSync$HR2,threshold)
PairTurn$HR2=PairTurn$HR2=removeOuts(PairTurn$HR2,threshold)

PairCon$Resp1=PairCon$Resp1=removeOuts(PairCon$Resp1,threshold)
PairSync$Resp1=PairSync$Resp1=removeOuts(PairSync$Resp1,threshold)
PairTurn$Resp1=PairTurn$Resp1=removeOuts(PairTurn$Resp1,threshold)
PairCon$Resp2=PairCon$Resp2=removeOuts(PairCon$Resp2,threshold)
PairSync$Resp2=PairSync$Resp2=removeOuts(PairSync$Resp2,threshold)
PairTurn$Resp2=PairTurn$Resp2=removeOuts(PairTurn$Resp2,threshold)


#Scaling the signals

PairCon$Resp1S=scale(PairCon$Resp1) 
PairCon$Resp2S=scale(PairCon$Resp2)  
PairCon$HR1S=scale(PairCon$HR1)
PairCon$HR2S=scale(PairCon$HR2)

PairSync$Resp1S=scale(PairSync$Resp1) 
PairSync$Resp2S=scale(PairSync$Resp2)  
PairSync$HR1S=scale(PairSync$HR1)
PairSync$HR2S=scale(PairSync$HR2)

PairTurn$Resp1S=scale(PairTurn$Resp1) 
PairTurn$Resp2S=scale(PairTurn$Resp2)  
PairTurn$HR1S=scale(PairTurn$HR1)
PairTurn$HR2S=scale(PairTurn$HR2)

#Creating new plots

#Creating plots for respiration
plot7=ggplot(PairCon, aes(x=time, y=Resp1S)) + geom_line(color="blue4") + geom_line(aes(x=time, y=Resp2S), color="firebrick3") + theme(legend.position="none")

plot7

plot8=ggplot(PairTurn, aes(x=time, y=Resp1S)) + geom_line(color="blue4") + geom_line(aes(x=time, y=Resp2S), color="firebrick3") + theme(legend.position="none")

plot9=ggplot(PairSync, aes(x=time, y=Resp1S)) + geom_line(color="blue4") + geom_line(aes(x=time, y=Resp2S), color="firebrick3") + theme(legend.position="none")

#Creating plots for heart rate
plot10=ggplot(PairCon, aes(x=time, y=HR1S)) + geom_line(color="coral") + geom_line(aes(x=time, y=HR2S), color="cyan4") + theme(legend.position="none")

plot11=ggplot(PairTurn, aes(x=time, y=HR1S)) + geom_line(color="coral") + geom_line(aes(x=time, y=HR2S), color="cyan4") + theme(legend.position="none")

plot12=ggplot(PairSync, aes(x=time, y=HR1S)) + geom_line(color="coral") + geom_line(aes(x=time, y=HR2S), color="cyan4") + theme(legend.position="none")

grid.arrange(plot7, plot8, plot9)

grid.arrange(plot10, plot11, plot12)


#Making a loop to find optimal parameters

DimensionResp=NULL
RadiusResp=NULL
DelayResp=NULL
DimensionHR=NULL
RadiusHR=NULL
DelayHR=NULL
n=1

files=list(PairCon, PairSync, PairTurn)

 par = list(lgM =  50, steps = seq(1, 6, 1),  radiusspan = 100,
  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,
  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,
  fnnpercent = 10,  typeami = "mindip") 

 
for (file in files){
  ans_resp=try(optimizeParam(file$Resp1S, file$Resp2S, par, min.rec= 2,
                     max.rec=8))
  
  if (length(ans_resp) > 1) {
  
  DimensionResp[n]=ans_resp$emddim
  RadiusResp[n]=ans_resp$radius
  DelayResp[n]=ans_resp$delay
  } 
  
  else {
    DimensionResp[n] = NA
    RadiusResp[n] = NA
    DelayResp[n] = NA
    
  }
  
  ans_HR=try(optimizeParam(file$HR1S, file$HR2S, par, min.rec= 2,
                     max.rec=8))
  
  if (length(ans_HR) > 1) {
  
  DimensionHR[n]=ans_HR$emddim
  RadiusHR[n]=ans_HR$radius
  DelayHR[n]=ans_HR$delay
  } 
  
  else {
    DimensionHR[n] = NA
    RadiusHR[n] = NA
    DelayHR[n] = NA
    
  }
  
   
   n=n+1
}

ParametersResp =data.frame(DimensionResp, RadiusResp, DelayResp)
ParameterHR=data.frame(DimensionHR, RadiusHR, DelayHR)

mean(ParametersResp$Dimension, na.rm = TRUE)
#2
mean(ParametersResp$Delay, na.rm = TRUE)
#28
mean(ParametersResp$Radius, na.rm = TRUE)
#0.3778

#Recurrence quantification analysis
SyncCrqa=crqa(PairSync$Resp1S, PairSync$Resp2S, delay=28, embed=2, radius=0.3778,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

#Representing the plot
RP=SyncCrqa$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP))
cols = c("white","blue4")
image(RP, xlab = "", ylab = "", col = cols) 


#Exploring lags of coordination
Profile=drpdfromts(PairSync$Resp1S, PairSync$Resp2S,datatype = 'continuous',ws=50,radius=0.3778)
timecourse = round( seq(-5000,5000,100)/1000, digit = 1) 
maxlag = Profile$maxlag/1000 
profile = Profile$profile*100 
Prof=data.frame(profile) 
ggplot(Prof, aes(timecourse,profile))+geom_line()+ geom_vline(xintercept = timecourse[maxlag], colour='red')
```

### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.
- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

```{r}


#Creating a filelist
filelist=list.files(path = "CleanData", pattern = ".csv")

preprocessing=function(data) {
  data = data %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))
  
  data$HR2=data$HR2=removeOuts(data$HR2,threshold)
  data$HR1=data$HR1=removeOuts(data$HR1,threshold)
  data$Resp2=data$Resp2=removeOuts(data$Resp2,threshold)
  data$Resp1=data$Resp1=removeOuts(data$Resp1,threshold)
  
  data$Resp1=scale(data$Resp1) 
  data$Resp2=scale(data$Resp2)  
  data$HR1=scale(data$HR1)
  data$HR2=scale(data$HR2)
  
  return(data)

}

FinalData=data.frame()
n=1
#Making a loop
for (file in filelist){
  data=read_csv(paste0("CleanData/", file))
  Datafile=preprocessing(data)
  Datafile$filename = filelist[n]
  
  write.csv(Datafile, file = paste0(file))

  par = list(lgM =  50, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")

  ans_resp=try(optimizeParam(Datafile$Resp1, Datafile$Resp2, par, min.rec= 2,
                     max.rec=8))

  if (length(ans_resp) > 1) {

  Datafile$Dimension_Resp=ans_resp$emddim
  Datafile$Radius_Resp=ans_resp$radius
  Datafile$Delay_Resp=ans_resp$delay
  }

  else {
    Datafile$Dimension_Resp = NA
    Datafile$Radius_Resp = NA
    Datafile$Delay_Resp = NA

  }

    ans_HR=try(optimizeParam(Datafile$HR1, Datafile$HR2, par, min.rec= 2,
                     max.rec=8))

  if (length(ans_HR) > 1) {

  Datafile$DimensionHR=ans_HR$emddim
  Datafile$RadiusHR=ans_HR$radius
  Datafile$DelayHR=ans_HR$delay
  }

  else {
    Datafile$DimensionHR = NA
    Datafile$RadiusHR = NA
    Datafile$DelayHR = NA

  }

  HRplot=ggplot(Datafile, aes(x=time, y=HR1)) + geom_line(color="coral") + geom_line(aes(x=time, y=HR2), color="cyan4") + theme(legend.position="none")
  RESPplot=ggplot(Datafile, aes(x=time, y=Resp1)) + geom_line(color="blue4") + geom_line(aes(x=time, y=Resp2), color="firebrick3") + theme(legend.position="none")

  FinalPlot=grid.arrange(HRplot,RESPplot)

  ggsave(paste0(file, ".png"), plot=FinalPlot, path="Plot")

  FinalData=rbind(FinalData, Datafile)
   
  n=n+1

}


# To get column with study number

for (file in 1:nrow(FinalData)){
  if (grepl("Study1", FinalData$filename[file])){
    FinalData$Study[file] = 1}
  if (grepl("Study2", FinalData$filename[file])){
    FinalData$Study[file] = 2}
}

# To get group number
FinalData$Group=regmatches(FinalData$filename, regexpr("[G].*[0-9]", FinalData$filename))

FinalData$Group = gsub("[G, _, T]", "", FinalData$Group)

FinalData$Group=substr(FinalData$Group, 1, nchar(FinalData$Group)-1)

# To get trial number
FinalData$Trial=regmatches(FinalData$filename, regexpr("[T].*[0-9]", FinalData$filename))

FinalData$Trial = gsub("[T]", "", FinalData$Trial)

# To get condition
FinalData = FinalData %>% group_by(filename) %>% mutate(Condition = gsub('.{4}$', '', strsplit(filename, "_")[[1]][4]))

# To get mean parameters for CRQA
mean(FinalData$Dimension_Resp, na.rm = TRUE) # 3.12 = 3
mean(FinalData$Radius_Resp, na.rm = TRUE) # 0.596
mean(FinalData$Delay_Resp, na.rm = TRUE) # 28.81 = 29

mean(FinalData$DimensionHR, na.rm = TRUE) # 14.24 = 14 
mean(FinalData$RadiusHR, na.rm = TRUE) # 1.274
mean(FinalData$DelayHR, na.rm = TRUE) # 21.39 = 21


#Exluding data from Study1_G1_T1_Synchronous.csv, Study1_G1_T2_TurnTaking.csv, Study1_G2_T1_TurnTaking.csv, Study1_G2_T2_Synchronous.csv, after looking at plots for all data

FinalData=FinalData[FinalData$filename != "Study1_G1_T1_Synchronous.csv",]
FinalData=FinalData[FinalData$filename != "Study1_G1_T2_TurnTaking.csv",]
FinalData=FinalData[FinalData$filename != "Study1_G2_T1_TurnTaking.csv",]
FinalData=FinalData[FinalData$filename != "Study1_G2_T2_Synchronous.csv",]

#Saving to a csv file
write.csv(FinalData, "FinalData.csv")

FinalData=read.csv("FinalData.csv")
FinalData=FinalData[-1]

# To get mean parameters for CRQA
mean(FinalData$Dimension_Resp, na.rm = TRUE) # 3.19 = 3
mean(FinalData$Radius_Resp, na.rm = TRUE) # 0.614
mean(FinalData$Delay_Resp, na.rm = TRUE) # 28.81 = 29

mean(FinalData$DimensionHR, na.rm = TRUE) # 11.95 = 12 
mean(FinalData$RadiusHR, na.rm = TRUE) # 1.633
mean(FinalData$DelayHR, na.rm = TRUE) # 29.88 = 30

#Radius changed in order to get a better RR

CRQA = function(data) {
  RespCRQA = crqa(data$Resp1, data$Resp2, delay = 29, embed = 3,
                   radius = 0.8, normalize = 0, rescale = 0,
                   mindiagline = 2, minvertline = 2)
  RespCRQA$RP = NULL  # Remove large matrix
  RespCRQA = as_tibble(RespCRQA) %>%
    mutate(type = 'Resp')
  
  HrCRQA = crqa(data$HR1, data$HR2, delay = 30, embed = 12,
                radius = 2.6, normalize = 0, rescale = 0,
                mindiagline = 2, minvertline = 2)
  HrCRQA$RP = NULL  # Remove large matrix
  HrCRQA = as_tibble(HrCRQA) %>%
    mutate(type = 'HR')
  
  return(rbind(RespCRQA, HrCRQA))
  
}


crqa_results = FinalData %>%
  dplyr::select(-c(.groups)) %>%  # Remove .groups (not needed right?)
  dplyr::group_by(filename) %>%  # Group by each file
  dplyr::do(CRQA(.)) %>%  # Do CRQA on each group (file)
  dplyr::ungroup()  # Ungroup (prob. not needed, didn't check) 

#Merging the results from the crqa analysis to the FinalData
FinalData1 = base::merge(FinalData, crqa_results, by = "filename")

#Saving to a csv file
write.csv(FinalData1, "FinalData1.csv")

FinalData1=read.csv("FinalData1.csv")
FinalData1=FinalData1[-1]
```

### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs
 
```{r}

CRQA_shuffled = data.frame()
n=1
#Creating a filelist
filelist2=list.files(path = "PreprocessedData", pattern = ".csv")

for (file in filelist2) {
  d=read_csv(paste0(path = "PreprocessedData/",file))
  
  d$HR1 = sample(d$HR1)
  d$HR2 = sample(d$HR2)
  d$Resp1 = sample(d$Resp1)
  d$Resp2 = sample(d$Resp2)
  
  data=CRQA(d)
  
  data$filename = filelist2[n]
  
  CRQA_shuffled=rbind(data, CRQA_shuffled)
  
  n=n+1
  
}

crqa_results$CRQA="Normal"
CRQA_shuffled$CRQA="Shuffled_control"

CRQA_Data=rbind(crqa_results, CRQA_shuffled)
CRQA_HR=subset(CRQA_Data[CRQA_Data$type=="HR",])
CRQA_Resp=subset(CRQA_Data[CRQA_Data$type=="Resp",])

Model1=lm(L~CRQA, CRQA_HR)
summary(Model1)

Model2=lm(L~CRQA, CRQA_Resp)
summary(Model2)

Model3=lm(RR~CRQA, CRQA_HR)
summary(Model3)

Model4=lm(RR~CRQA, CRQA_Resp)
summary(Model4)

Model5=lm(ENTR~CRQA, CRQA_HR)
summary(Model5)

Model6=lm(ENTR~CRQA, CRQA_Resp)
summary(Model6)
```
 
### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs

```{r}
setwd("~/Desktop/3. Semester/Experimental methods 3/Portfolio 4/PreprocessedALL")

prepro_filelist = list.files(pattern = "Study1")

num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.


# Per each condition
for (co in c("Synchronous","TurnTaking","SelfPaced")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list
    
  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study1_G',SurrogateList$a[i]) #Insert group number from Surrogatelist 
  f2=paste0('Study1_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2)
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write_csv(d3,file.path("surrogate",file3))
  write_csv(d4,file.path("surrogate",file4))
  write_csv(d5,file.path("surrogate",file5))
  write_csv(d6,file.path("surrogate",file6))
  }
}

prepro_filelist = list.files(pattern = "Study2")

num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.


# Per each condition
for (co in c("Synchronous","TurnTaking","Conversation")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list
    
  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study2_G',SurrogateList$a[i]) #Insert group number from Surrogatelist 
  f2=paste0('Study2_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2)
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write_csv(d3,file.path("surrogate",file3))
  write_csv(d4,file.path("surrogate",file4))
  write_csv(d5,file.path("surrogate",file5))
  write_csv(d6,file.path("surrogate",file6))
  }
}

setwd("~/Desktop/3. Semester/Experimental methods 3/Portfolio 4")

CRQA_surrogate = data.frame()
n=1
#Creating a filelist
filelist3=list.files(path = "surrogate", pattern = ".csv")

for (file in filelist3) {
  d=read_csv(paste0(path = "surrogate/",file))
  
  data=CRQA(d)
  
  data$filename = filelist3[n]
  
  CRQA_surrogate=rbind(data, CRQA_surrogate)
  
  n=n+1
  
}

CRQA_surrogate$CRQA="Surrogate"

write.csv(CRQA_surrogate, "CRQA_surrogate.csv")

CRQA_Data1=rbind(crqa_results, CRQA_surrogate)
CRQA_HR1=subset(CRQA_Data1[CRQA_Data1$type=="HR",])
CRQA_Resp1=subset(CRQA_Data1[CRQA_Data1$type=="Resp",])


#Making models to compare the surrogate pairs to the controls
Model7=lm(L~CRQA, CRQA_HR1)
summary(Model7)

Model8=lm(L~CRQA, CRQA_Resp1)
summary(Model8)

Model9=lm(RR~CRQA, CRQA_HR1)
summary(Model9)

Model10=lm(RR~CRQA, CRQA_Resp1)
summary(Model10)

Model11=lm(ENTR~CRQA, CRQA_HR1)
summary(Model11)

Model12=lm(ENTR~CRQA, CRQA_Resp1)
summary(Model12)
```

### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?

Could include as a baseline maybe. Could substract the effects of doing the same tasks and being in the same surroundings from the actual "personal" coordination. 

```{r}
# To get column with study number
for (file in 1:nrow(crqa_results)){
  if (grepl("Study1", crqa_results$filename[file])){
    crqa_results$Study[file] = 1}
  if (grepl("Study2", crqa_results$filename[file])){
    crqa_results$Study[file] = 2}
}

# To get group number
crqa_results$Group=regmatches(crqa_results$filename, regexpr("[G].*[0-9]", crqa_results$filename))

crqa_results$Group = gsub("[G, _, T]", "", crqa_results$Group)

crqa_results$Group=substr(crqa_results$Group, 1, nchar(crqa_results$Group)-1)

# To get trial number
crqa_results$Trial=regmatches(crqa_results$filename, regexpr("[T].*[0-9]", crqa_results$filename))

crqa_results$Trial = gsub("[T]", "", crqa_results$Trial)

# To get condition
crqa_results$filename=as.character(crqa_results$filename)
crqa_results = crqa_results %>% group_by(filename) %>% mutate(Condition = gsub('.{4}$', '', strsplit(filename, "_")[[1]][4]))

# To subset data into heart rate and respiration data
CRQAresults_Resp=subset(crqa_results[crqa_results$type == "Resp",])
CRQAresults_HR=subset(crqa_results[crqa_results$type == "HR",])

Model_RR_HR=lmer(RR ~ Condition + (1|Study) + (1|Group) , CRQAresults_HR)
summary(Model_RR_HR)

Model_L_resp=lmer(L ~ Condition + (1|Study) + (1|Group) , CRQAresults_Resp)
summary(Model_L_resp)

Model_L_HR=lmer(L ~ Condition + (1|Study) + (1|Group) , CRQAresults_HR)
summary(Model_L_HR)

Model_ENTR_resp=lmer(ENTR ~ Condition + (1|Study) + (1|Group) , CRQAresults_Resp)
summary(Model_ENTR_resp)

Model_ENTR_HR=lmer(ENTR ~ Condition + (1|Study) + (1|Group) , CRQAresults_HR)
summary(Model_ENTR_HR)
```

### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them